### 2022-05-24 paper.Rmd
working on example

Here, the variable `features` has to be a data table containing the image data: 900 rows representing images; 3 columns representing the features beauty, arousal, and valence. The accompanying OSF repository contains the fully reproducible code that includes downloading and reading the OASIS data, selecting the relevant columns, and finally storing them in the `features` variable (**TODO**). The `kplus_anticlustering()` function has four boolean arguments to specify whether variance, skewness, kurtosis and covariances should be included as part of the k-plus criterion. Only the argument `variance` is set to `TRUE` by default; the other arguments have to be "turned on". If other higher order moments should be included as part of the optimization, the argument `moments` can be used to specify the desired moments as an integer vector.

@@

@@

  K <- 9
  mean_sd_tabs <- list()
  for (criterion in c("kplus", "variance", "diversity")) {
    oasis[[paste(criterion, "group", sep = "_")]] <- anticlustering(
      features,
      standardize = TRUE,
      K = K,
      objective = criterion,
      method = "local-maximum"
    )
    mean_sd_tabs[[criterion]] <- mean_sd_tab(
      features,
      oasis[[paste(criterion, "group", sep = "_")]]
    )
    mean_sd_tabs[[criterion]] <- cbind(
      1:K,
      nrow(features) / K,
      mean_sd_tabs[[criterion]]
    )
  }

>>>>

Here, the variable `features` has to be a data table containing the image data: 900 rows representing images; 3 columns representing the features beauty, arousal, and valence. The accompanying OSF repository contains the fully reproducible code that includes downloading and reading the OASIS data, selecting the relevant columns, and finally storing them in the `features` variable (**TODO**). The `kplus_anticlustering()` function has four boolean arguments to specify whether variance, skewness, kurtosis and covariances should be included as part of the k-plus criterion. Only the argument `variance` is set to `TRUE` by default; the other arguments have to be "turned on". If other higher order moments should be included as part of the optimization, the optional argument `moments` can be used to specify the desired moments as an integer vector.

@@

```{r, eval = FALSE}

@@

  K <- 9
  for (criterion in c("kplus", "variance", "diversity")) {
    if (criterion == "kplus") {
        oasis[[paste(criterion, "group", sep = "_")]] <- kplus_anticlustering(
            features,
            K = K,
            variance = TRUE,
            skew = TRUE,
            kurtosis = FALSE,
            covariances = FALSE,
            moments = NULL,
            method = "local-maximum",
            standardize = TRUE
        )
    } else {
        oasis[[paste(criterion, "group", sep = "_")]] <- anticlustering(
            features,
            standardize = TRUE,
            K = K,
            objective = criterion,
            method = "local-maximum"
        )
    }

  }

    descriptive_by_group <- function(features, anticlusters, FUN, name) {
    df <- data.frame(
      t(data.frame(lapply(by(features, anticlusters, FUN), c)))
    )
    df$group <- 1:nrow(df)
    df$Descriptive = name
    df
  }

  descriptive_by_group_all <- function(features, anticlusters) {
    means <- descriptive_by_group(features, anticlusters, colMeans, "mean")
    sds <- descriptive_by_group(
      features, 
      anticlusters, 
      function(x) sapply(x, sd),
      "sds"
    )
    skew <- descriptive_by_group(
      features, 
      anticlusters, 
      function(x) sapply(x, DescTools::Skew),
      "skew"
    )
    rbind(means, sds, skew)
  }

kplus <- descriptive_by_group_all(features, oasis$kplus_group)
kplus <- data.frame(kplus, Objective = "kplus")

kmeans <- descriptive_by_group_all(features, oasis$variance_group)
kmeans <- data.frame(kmeans, Objective = "kmeans")
diversity <- descriptive_by_group_all(features, oasis$variance_group)
diversity <- data.frame(diversity, Objective = "diversity")

all_objs <- rbind(kplus, kmeans, diversity) %>% 
  pivot_wider(names_from = Descriptive, values_from = c(beauty_mean, Valence_mean, Arousal_mean))

  # append all tables to the same table:
  rownames(all_objs) <- NULL
  colnames(all_objs) <- c("Group", "N", "Beauty", "Valence", "Arousal")
